---
title: "Data Processing Scheme"
author: "YJH"
date: "11/20/2020"
output: html_document
---
- Please use R version of 3.6.1 (2019-07-05)

# Environment control
- You just need to run this chunk once! Before you did this, please check https://rstudio.github.io/renv/articles/renv.html for details using renv package to control package version.

```{r}
if(!require("renv")) install.packages("renv")

# initialize a new project
renv::init() # Choose 2 if you run this line twice

# Install and library the packages
## Clear the variable and all packages
rm(list = ls())
lapply(names(sessionInfo()$otherPkgs), function(pkgs)
  detach(
    paste0('package:', pkgs),
    character.only = T,
    unload = T,
    force = T
  ))
(.packages())

install.packages("magrittr")
install.packages("readr")
install.packages("dplyr")
install.packages("tidyr")
install.packages("tidyverse")
install.packages("openxlsx")

install.packages("purrr")
install.packages("stringr")
install.packages("ggplot2")
install.packages("cowplot")
install.packages("caret")
install.packages("cowplot")
install.packages("corrplot")
install.packages("DALEX")
install.packages("DescTools")
install.packages("doParallel")
install.packages("GGally")
install.packages("Rmisc")
install.packages("PupillometryR")
install.packages("inspectdf")
install.packages("vcd")
install.packages("ggpubr")
install.packages("ggmosaic")
install.packages("scales")
install.packages("ggridges")
install.packages("viridis")

install.packages("lattice")
install.packages("MASS")
install.packages("nnet")
install.packages("mice")
install.packages("missForest")

# Avoid package conflict
select <- dplyr::select
mutate <- dplyr::mutate
summarise <- dplyr::summarise
summarize <- dplyr::summarize

renv::status()   # check sttatus
renv::snapshot() # create a lockfile capturing the state of a project's R package dependencies. The lockfile can be used to later restore these project's dependencies as required.
```

# Data scheme

## Input
```{r}
# Restore the package
## Remove everything except base package
rm(list = ls())
lapply(names(sessionInfo()$otherPkgs), function(pkgs)
  detach(
    paste0('package:', pkgs),
    character.only = T,
    unload = T,
    force = T
  ))
(.packages())

## Restore package we stored in the "Environment control" section.
renv::restore()

## For data processing
if(!require("magrittr")) install.packages("magrittr")
if(!require("readr")) install.packages("readr")
if(!require("dplyr")) install.packages("dplyr")
if(!require("tidyr")) install.packages("tidyr")
if(!require("tidyverse")) install.packages("tidyverse")
if(!require("openxlsx")) install.packages("openxlsx")

## For visulization
if(!require("purrr")) install.packages("purrr")
if(!require("stringr")) install.packages("stringr")
if(!require("ggplot2")) install.packages("ggplot2")
if(!require("cowplot")) install.packages("cowplot")
if(!require("caret")) install.packages("caret")
if(!require("cowplot")) install.packages("cowplot")
if(!require("corrplot")) install.packages("corrplot")
if(!require("DALEX")) install.packages("DALEX")
if(!require("DescTools")) install.packages("DescTools")
if(!require("doParallel")) install.packages("doParallel")
if(!require("GGally")) install.packages("GGally")
if(!require("Rmisc")) install.packages("Rmisc")
if(!require("PupillometryR")) install.packages("PupillometryR")
if(!require("inspectdf")) install.packages("inspectdf")
if(!require("vcd")) install.packages("vcd")
if(!require("ggpubr")) install.packages("ggpubr")
if(!require("ggmosaic")) install.packages("ggmosaic")
if(!require("scales")) install.packages("scales")
if(!require("ggridges")) install.packages("ggridges")
if(!require("viridis")) install.packages("viridis")

## For missing value handle
if(!require("lattice")) install.packages("lattice")
if(!require("MASS")) install.packages("MASS")
if(!require("nnet")) install.packages("nnet")
if(!require("mice")) install.packages("mice")
if(!require("missForest")) install.packages("missForest")

(.packages())

# Data Input
## Please run setwd("~/yourdir/bank-marketing-strategy-analysis/code") (change yourdir to yours).
## Then, all the file dictionary work.
bank <- read_delim("../data/origin/bank-additional/bank-additional-full.csv", ";", 
                   escape_double = FALSE, trim_ws = TRUE)

# Plotting theme
text_theme = theme(
                plot.title = element_text(face="bold",
                                          hjust = 0.5,
                                          size = 16),
                plot.subtitle = element_text(face="bold", 
                                             hjust = 0.5,
                                             size = 4,
                                             margin = c(t = 13, r = 0, b = 17, l = 0)),
                axis.title = element_text(size=14),
                legend.title = element_text(size=14))

colors <- c("#E69F00", "#56B4E9", "#009E73","#d9a99e",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7",
          "#F4EDCA",  "#9a3820",  "#a7a97c")
```

## Data Description
```{r}
source("../code/funcs.R")
my_glimpse(file = "../tables/part2/data_report.xlsx")
```

### Discrete variables
```{r}
if_plot = F # Switch upon plotting+data processing or only data processing.
if(if_plot){
  inspect_cat(bank, show_plot = TRUE)}
```

### Continuous variables
```{r}
# Single Plot
if(if_plot){
bank %>% keep(is.numeric) %>% colnames -> temp
bank %>%
  select(c(y,temp)) %>%
  pivot_longer(temp,'key',values_to = 'value') %>%
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free", ncol=5,nrow=2) +
    geom_histogram(aes(fill=y)) +
  theme(axis.text.x = element_text(angle = -45, vjust = 0.5),legend.position = "bottom") +
    scale_fill_manual("Result", values =colors,na.value = "#5f5f5f") +
  
    labs(x=NULL,y=NULL) #+ theme_pubr()

# Pair Plot
my_cor = function(data, mapping, alignPercent = 0.6, method = "pearson", 
    use = "complete.obs", corAlignPercent = NULL, corMethod = NULL, 
    corUse = NULL, ...) {
  return(GGally::ggally_cor(data, mapping)+theme(panel.grid.minor = element_blank(), 
        panel.grid.major = element_blank())) 
}

smooth <- function(data, mapping, method = "loess",formula = 'y ~ x', ...) {
  p <- ggplot(data = data, mapping = mapping) +
    geom_point(...,alpha=0.14) +
    geom_smooth(...,method = method,formula = formula,size = 1,...)
  
  p
}
smooth_lm <- function(data, mapping, method = "lm",formula = 'y ~ x', ...) {
  p <- ggplot(data = data, mapping = mapping) +
    geom_point(...,alpha=0.14) +
    geom_smooth(...,method = method,formula = formula,size = 1,...)
  p
}

bank %>% select(where(is.numeric)) %>% colnames -> numeric_vars
bank %>% select(c("y", numeric_vars)) %>%
  ggpairs(aes(color=y),
            upper = list(continuous = smooth_lm,
                         combo = "dot", 
                         discrete = "box", 
                         na = "na"),
            lower = list(continuous = my_cor, 
                         combo = "box_no_facet", 
                         discrete = "facetbar", 
                         na = "na"),switch="y",cardinality_threshold = 16) -> p
}
```

## Data Cleaning
### Remove repeated data
```{r}
# Detact lines repeated
#View(bank %>% group_by_at(colnames(.)) %>% filter(n()>1)) #12 lines are unusally repeated, given the rear chances.
bank %<>% unique
```

### Data Wrangling
```{r}
# unknown to na
## Detact
treat_temp = c()
for(i in colnames(bank)){
  if("unknown" %in% (bank %>% distinct_at(i) %>% pull(1))){
    treat_temp %<>% append(i)
  }
}
print("unknown:")
print(paste0(treat_temp,collapse = "、"))

## Replace
bank %<>% mutate_at(
  vars(treat_temp), 
  funs(str_replace(., c("unknown"), NA_character_)))

# Unify data type
unify_type <- function(df){
  df %>%
    # discreate as factor
    mutate_if(sapply(df, is.character), as.factor) %>%
    # continuous as numeric
    mutate_if(sapply(df, is.integer), as.numeric)
}
bank %<>% unify_type

# Replace 999 pdays as NA
bank %<>% mutate(pdays= ifelse(pdays==999,NA,pdays))

# Replace yes/no with 0/1
## Detact yes/no only
yesno_to_10 <- function(df){
  treat_temp = c()
  for(i in colnames(df)){
    if("yes" %in% (df %>% distinct_at(i) %>% pull(1))){
      treat_temp %<>% append(i)
    }
  }
  # yes/no换成0/1
  df %>%
    mutate_at(treat_temp,
              ~case_when(. %in% "yes" ~ 1, . %in% "no" ~ 0)) %>%
    unify_type
}
```


## EDA and feature engineering
- Helping function
```{r}
glimpsedata <- function(){
  return(glimpse(bank))
}

if_plot = F
save_plot = F

eda_cata <- function(group, data=bank){
  print(table(bank %>% dplyr::select(!!sym(group)),useNA="ifany"))
  group = group
  if(if_plot){
  layout <- matrix(c(1,1,1,1,4,4,4,0,0,
                     1,1,1,1,4,4,4,3,3,
                     2,2,2,2,4,4,4,3,3,
                     2,2,2,2,4,4,4,0,0), nrow = 4, byrow=TRUE)
    # plot1
     data %>% 
      ggplot(aes(x = !!sym(group), 
                 fill = factor(y))) + 
      geom_bar(position = "stack") -> p1
    
    # plot 2
    data %>% 
      ggplot(aes(x = !!sym(group), 
             fill = factor(y))) + 
    geom_bar(position = "fill") -> p2
    
    # plot3
    data %>%
      dplyr::select(temp = !!sym(group)) %>%
      group_by(temp) %>%
      dplyr::summarise(percent = n()) %>% ungroup %>%
      mutate(percent = percent/sum(percent)) %>%
      
      ggplot(aes(x="", y = percent, fill = temp)) +
      geom_bar(width = 1, stat = 'identity') +
      coord_polar("y", direction = -1) +
      theme_void()+ ylab(group) +
      geom_text(aes(label = percent),
                position = position_stack(vjust=0.5)) +
      scale_fill_discrete(name=group) -> p3
    
    # plot 4
    data %>%
      dplyr::select(temp = !!sym(group),y) %>%
      group_by(temp,y) %>%
      dplyr::summarise(percent = n()) %>% 
      group_by(y) %>%
      dplyr::summarise(temp=temp,percent = percent/sum(percent))  %>%
    
    ggplot(aes(x = y, y = percent, fill = temp, label = temp)) +
      geom_bar(stat = "identity") + ylab(group) +
      geom_text(position = position_stack(vjust=0.5)) -> p4
 
  
    multiplot(p1,p2,p3,p4,layout=layout)
  }
    
  if(save_plot){
    png(paste0("../images/每个变量与Y/",group,"_分类型图.png"),width=1500,height=485)
    multiplot(p1,p2,p3,p4,layout=layout)
    dev.off()
  }
}

eda_num <- function(var,data=bank){
  if(if_plot){
  ggplot(data = data, 
       aes(x = factor(y), y = !!sym(var))) + #
  geom_flat_violin(aes(fill = factor(y)),
                   position = position_nudge(x = .2, y = 0), 
                   trim = TRUE, 
                   alpha = .4, 
                   scale = "width") +
  geom_point(aes(y = !!sym(var), color = factor(y)), 
             position = position_jitter(w = .15, h = 0.000000000002), 
             size = .001, 
             alpha = 0.4) +
  geom_boxplot(width = .3, 
               outlier.shape = NA,
               alpha = 0.5) +
  labs(x="Result") + 
  coord_flip() +
  scale_fill_manual(c("fail", "success"), values =colors,na.value = "#5f5f5f") +
  scale_color_manual(c("fail", "success"), values =colors,na.value = "#5f5f5f") +
  
  expand_limits(x = 3) +
      theme_pubr()-> p
  
   #print(p)
   return(p)
  }
  if(save_plot){
    ggsave(plot = p, filename = paste0("../images/X-withY/",var,"_continuous.png"),width=15,height=4.85)
  }
}

eda_cata_num <- function(group, var, data=bank,flip = F,expand_limits=5.2, x_angle = 45){
  plot =NA
  if(if_plot){
  ggplot(data = bank, 
       aes(x = as.factor(!!sym(group)), y = !!sym(var), fill = y)) + #
  geom_flat_violin(position = position_nudge(x = .2, y = 0), 
                   trim = TRUE, 
                   alpha = .4, 
                   scale = "width") +
  geom_point(aes(y = !!sym(var), color = factor(y)), 
             position = position_jitter(width = .15), 
             size = .5, 
             alpha = 0.1) +
  geom_boxplot(width = .3, 
               outlier.shape = NA,
               alpha = 0.5) +
  expand_limits(x = expand_limits) +
  labs(x = group, y = var) +
  guides(color=NULL, fill=guide_legend(title="Result:")) +
  scale_fill_manual(#c("fail", "success"), 
                           values =colors,na.value = "#5f5f5f")+
  scale_color_manual(#c("fail", "success"), 
                     values =colors,na.value = "#5f5f5f")+
  guides(color=NULL) +
  theme_pubr(base_size = 11, x.text.angle = x_angle) -> plot
  if(flip){
    plot = plot + coord_flip()
  }
  return(plot)
  }
}
see = function(data){
  View(data)
}

eda_withy <- function(var, data = bank, flip=F){
  plot = NA
  if(if_plot){
  if(is.numeric(data %>% dplyr::select(!!sym(var)) %>%pull(1))){
      data %>%
        mutate(y = factor(y)) %>%
      
      ggplot(aes(x = as.factor(y), y = !!sym(var))) + #
          geom_flat_violin(position = position_nudge(x = .2, y = 0), 
                           trim = TRUE, 
                           alpha = .4, 
                           scale = "width") +
          geom_point(aes(y = !!sym(var), color = as.factor(y)), 
                     position = position_jitter(w = .15, h = 0.000000000002), 
                     size = .001, 
                     alpha = 0.4) +
          geom_boxplot(width = .3, 
                       outlier.shape = NA,
                       alpha = 0.5) +
          scale_x_discrete("Result", labels = c("yes" = "success", "no" = "fail")) +
          scale_color_manual(labels = c("success", "fail"),values =colors[1:2]) +
          labs(color = "Result") +
          #coord_flip() +
          theme(legend.position = "none")+
          expand_limits(x = 3) + text_theme -> plot

  }
  if(is.factor(data %>% dplyr::select(!!sym(var)) %>% pull(1))){
  
      data %>%
        dplyr::select(temp = !!sym(var),y) %>%
        group_by(temp,y) %>%
        dplyr::summarise(percent = n()) %>% 
        group_by(y) %>%
        dplyr::summarise(temp=temp,percent = percent/sum(percent))  %>%
        mutate(y = factor(y)) %>%
      
      ggplot(aes(x = y, y = percent, fill = temp, label = temp)) +
        geom_bar(stat = "identity") + xlab(var) + ylab(paste0("% of ",var)) +
        scale_x_discrete("y", labels = c("yes" = "sucess", "no" = "fail")) +
        scale_y_continuous(labels = function(x) paste0(x*100, "%")) +
        scale_fill_manual(values =colors,na.value = "#5f5f5f") +
        guides(fill=guide_legend(title=var))+
        geom_text(position = position_stack(vjust=0.5)) +  text_theme -> plot
  }
  if(flip){
    plot = plot + coord_flip()
  }
  }
    return(plot)
}

eda_y <- function(data = bank){
  if(if_plot){
  data %>% 
    ggplot(aes(x = y)) + 
    geom_bar(position = "stack")
}
}
```

### Personal information
- First Draft
```{r}
# if(if_plot){
# eda_num("age")
# eda_cata("job")
# eda_cata("marital")
# eda_num("education")
# eda_cata("education", bank%>% mutate(education = factor(education)))
# eda_cata("default")
# eda_cata("housing", bank %>% mutate(housing = factor(housing)))
# eda_cata("loan",bank %>% mutate(loan = factor(loan)))
# 
# vcd::mosaic(~ education+housing +y+loan, data = temp, shade = TRUE,
#             labeling_args = list(abbreviate_labs = c(3, 10, 1)))}
```

#### Overall visualization
```{r}
if(if_plot){
multiplot(eda_withy("marital"),
          eda_withy("default"),
          eda_withy("loan"), 
          eda_withy("housing"),cols=4)}
if(if_plot){
multiplot(
          eda_withy("job"),
          eda_withy("education"),cols=2)}

#eda_withy("age")
```


#### Data processing and the reason doing that

##### Replace default==1 as a catogory
```{r}
if(if_plot){
eda_cata("default")

# Test
## Before:
bank %>%
  mutate(default = ifelse(is.na(default),"NA value",default)) -> temp1
vcd::mosaic(~ default + y, data = temp1, shade = TRUE)

## After:
bank %>% 
  mutate(default = ifelse(default=="no" & !is.na(default),"no","other")) -> temp2
vcd::mosaic(~ default + y, data = temp2, shade = TRUE)
}
# Conduct
bank <- temp2

```

##### Transform education as cordinal variiable
```{r}
if(if_plot){
# Before:
## Left plot:
vcd::mosaic(~ education + job, data = bank, shade = TRUE,
            labeling_args = list(abbreviate_labs = c(4, 3, 1)))
## Right plot:
bank %>%
  group_by(job, education) %>%
  dplyr::summarise(proportion = n()) %>% ungroup %>%
  mutate(proportion = proportion/sum(proportion)) %>%

ggplot( aes(x=education, y=job, fill=proportion, label=proportion)) +
  geom_tile() +
  scale_fill_gradient(low = "#56B4E922",high = colors[6]) +   theme_pubr(legend="right",x.text.angle = -20) +
  geom_text(aes(label = paste0(round(proportion*100,2),"%")),color="black", size=3.5) 
}

# After:
bank %>% 
  mutate(education = as.character(revalue(education, 
      c("professional.course" = 14, "university.degree" = 16, "high.school" = 12,
      "basic.9y" = 9, "basic.6y" = 6, "basic.4y" = 4, "illiterate" = 1)))) %>%
  mutate(education = as.numeric(education)) -> temp

if(if_plot){
ggplot(temp, aes(x = education, y = `job`, fill = ..x..)) +
  geom_density_ridges_gradient(na.rm=F,scale = 2, rel_min_height = 0.01, gradient_lwd = 0.04) +
  
  scale_x_continuous(limits=c(xmin=1,xmax=18),breaks= seq(0, 18, by=1)) +
  scale_fill_viridis(name = "Year of edu", direction = -1, option = "C") +
  theme_ridges(font_size = 13, grid = TRUE) + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(hjust = 0.5))
  }

# Conduct:
bank <- temp
```

##### Marriage: seperate them into yes/noo
```{r}
if(if_plot){
# Before
temp <- bank
vcd::mosaic(~ marital + y+education  , data = temp, shade = F,
            labeling_args = list(abbreviate_labs = c(10, 10, 0)))

vcd::mosaic(~ marital + y+job  , data = temp, shade = F,
             labeling_args = list(abbreviate_labs = c(10, 10, 1)))

vcd::mosaic(~ marital + y+ housing  , data = temp, shade = F,
            labeling_args = list(abbreviate_labs = c(10, 10, 1)))
}
# After
bank %>%
  mutate(marital = revalue(marital, c(
    'single' = '0',
    'married' = '1',
    'divorced'= '1'))) -> temp
if(if_plot){
  vcd::mosaic(~ marital + y+education  , data = temp, shade = T,
            labeling_args = list(abbreviate_labs = c(10, 10, 0)))

vcd::mosaic(~ marital + y+job  , data = temp, shade = T,
             labeling_args = list(abbreviate_labs = c(10, 10, 1)))

vcd::mosaic(~ marital + y+ housing  , data = temp, shade = T,
            labeling_args = list(abbreviate_labs = c(10, 10, 1)))

}

# Conduct:
bank %<>%
  mutate(marital = revalue(marital, c(
    'single' = '0',
    'married' = '1',
    'divorced'= '1')))
```

##### Keep age as original format
```{r}
# Before:
if(if_plot){
ggarrange(
  eda_cata_num("job","age",x_angle=0),
  eda_cata_num("education","age",x_angle=0),
  ncol=1,common.legend = T)
}
```


### Current campaign event

#### Extract year and month feature
```{r}
# Extract year
year_cur = 2008
year_col = c()
flag = 0
for(x in bank$month){
  if(x == 'mar' & flag != 1){
    year_cur = year_cur +1
    flag = 1
  }
  if(x == "apr"){
    flag = 0
  }
  year_col = append(year_col, year_cur)
}
bank$year <- year_col
bank %<>% relocate(year, .before=month)

# Effect Analysis
bank %<>% 
  mutate(month = as.character(month)) %>%
  mutate(month = as.numeric(revalue(month,c('apr'=4, 'aug'=8, 'dec'=12,
                   "jul"=7,"jun"=6,"mar"=3,"may"=5,"nov"=11,"oct"=10,"sep"=9))))

group = "month"

bank %>% nrow -> bank_nrow
prop.table(table(bank$y))[2] %>% as.vector() -> average_line

ggarrange(
  # left plot
  bank %>% 
    ggplot(aes(x = !!sym(group), fill = factor(y))) + 
    geom_bar(position = "stack") + 
    geom_label(stat = "count", 
               aes(label = ..count.., y = ..count..),
               size=3,
               fill=NA,
               position = position_dodge(0.9)) +
    labs(y="number of observations") + ggtitle("Observations") +
    scale_fill_manual(c("fail", "success"), values =colors,na.value = "#5f5f5f") +
    scale_x_continuous(limits=c(xmin=1,xmax=12),breaks= seq(0, 12, by=1)) +
    theme_pubr()+facet_grid(year~.)+ theme(panel.spacing = unit(2, "lines")),
    
  # right plot
  
  bank %>% 
    ggplot(aes(x = !!sym(group), fill = factor(y))) + 
    geom_bar(position = "fill") + ylab("percentage") +
    labs(y="number of observations") + ggtitle("% of success in Observations") +
    scale_y_continuous(labels = function(x) paste0(x*100, "%")) +
    scale_fill_manual(c("fail", "success"), values =colors,na.value = "#5f5f5f") +
    
    scale_x_continuous(limits=c(xmin=1,xmax=12),breaks= seq(0, 12, by=1)) +
    geom_hline(yintercept=average_line, linetype="dashed", color = colors[3]) +
    theme_pubr()+facet_grid(year~.)+ theme(panel.spacing = unit(2, "lines")),
  ncol = 2, common.legend = TRUE, legend="right")

```


```{r}
# Add monthly phone calls
bank %<>% group_by(year,month) %>%
  mutate(monthly_contacts = n()) %>% ungroup %>%
  relocate(monthly_contacts, .after = month)
eda_num("monthly_contacts")
```


#### day_of_week shows no pattern
```{r}
# Left plot
if(if_plot){
bank %<>% mutate(day_of_week = factor(day_of_week, levels = c("mon","tue","wed","thu","fri")))
bank %>% yesno_to_10() %>% filter(year<=2009)-> temp
vcd::mosaic(~ year +day_of_week+month+y  , data = temp, shade = TRUE,
            labeling_args = list(abbreviate_labs = c(4, 10, 4)))

# Right plot
group = "day_of_week"
bank %>% 
      ggplot(aes(x = !!sym(group), 
                 fill = y)) + 
      
      geom_bar(position = "fill") +
     scale_y_continuous(labels = function(x) paste0(x*100, "%")) +
        scale_fill_manual(values =colors,na.value = "#5f5f5f") +facet_grid(month~year) +
  theme_pubr(legend = "right")
}
# Delete day_of_week because it's unstable
bank %<>% dplyr::select(-day_of_week)
```

#### Keep contact but delete duration
```{r}
if(if_plot){
eda_cata("contact")
eda_withy("contact")
eda_cata_num("contact","duration",flip=T,expand_limits=3,x_angle = 0)
}
#bank %<>% dplyr::select(-duration)
```

### Last campaign
#### campaign is too discreted so we cut the tail
```{r}
cut = quantile(bank$campaign,0.9985)
bank %>% 
  mutate(campaign = ifelse(campaign < cut, campaign, cut)) -> temp

ggarrange(
  eda_num("campaign"),
  eda_num("campaign",temp),ncol=1,common.legend = T,legend = "right")
```

#### Delete pdays, as it's not accorded to the campagin
```{r}
table(bank$campaign,useNA = "ifany")
table(bank$pdays,useNA = "ifany")
bank %<>% select(-pdays)
```

#### Pick one from previous and poutcome
```{r}
table(bank$poutcome,useNA = "ifany")
table(bank$previous,useNA = "ifany")

# eda_num("previous")
# eda_cata("poutcome")
# eda_cata("previous", bank %>% mutate(previous = factor(previous)))

bank %>% 
  filter(previous>=1) %>% 
  filter(poutcome!="nonexistent") %>% mutate(poutcome=factor(poutcome)) -> temp

vcd::mosaic(~   previous+y+poutcome  , data = temp , shade = T,
            gp = gpar(fill = rep(c(colors[1],colors[3]),each=14)),
            labeling_args = list(abbreviate_labs = c(1, 10, 1)))
            
# A stange case of 7 phone but failed, delete it.
bank %>% filter(previous<7)
```


### Economics

#### Averaging
```{r}
subtract_time <- function(df){
  df %>% group_by(year,month) %>% 
    select(econs) %>%
    unique %>%
    mutate(month=as.character(str_pad(month, width = 2, pad = "0", side = "left"))) %>%
    mutate(time = paste0(year,"-",month,"-01")) %>%
    mutate(time = as.Date(time, "%Y-%m-%d"))%>%
    pivot_longer(econs, names_to = 'type',values_to = 'value')
}
# Before
econs = c("emp.var.rate","cons.price.idx","cons.conf.idx","cons.conf.idx","euribor3m","nr.employed")

bank %>% 
  subtract_time %>%
  ggplot(aes(x=time,y=value)) + geom_line(aes(color=type)) + 
    scale_x_date(date_labels="%Y-%m",date_breaks  ="1 month") +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
    facet_grid(type~.,scales="free")  -> p1

# After
bank %>% mutate_at(
  vars(econs),
  funs((.-mean(.))/sd(.))) -> temp

temp %>% 
  subtract_time %>%
  ggplot(aes(x=time,y=value)) + geom_line(aes(color=type)) + 
    scale_x_date(date_labels="%Y-%m",date_breaks  ="1 month") +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) -> p2

if(if_plot){
  ggarrange(p1,p2,ncol=2,common.legend = T)
}
```

```{r}
ggarrange(
eda_num(econs[1]),
eda_num(econs[2]),
eda_num(econs[3]),
eda_num(econs[4]),
eda_num(econs[5]),ncol=3,nrow=2,common.legend = T,legend.position = "right") 
```

## Data processing
```{r}
bank %<>% yesno_to_10
```

### Unify data
```{r}
bank %<>%
  # Discrete as factor
  mutate_if(sapply(bank, is.character), as.factor) %>%
  # Continuous as numeric
  mutate_if(sapply(bank, is.integer), as.numeric)
```

- Output Data
```{r}
bank %<>% relocate(year,.before=month)
```



### Missing value processing

```{r}
bank %<>%
  mutate_if(sapply(bank, is.character), as.factor) %>%
  mutate_if(sapply(bank, is.integer), as.numeric)

# Delete data that miss one of marital and job, and education.
bank %<>%
  filter(!((is.na(marital) | is.na(job)) & is.na(education)))

# Discovery: housing and loan miss the same 990 lines
bank %>%
  #filter(is.na(housing)) %>%
  filter(is.na(housing) | is.na(loan))

# Missing value counting
report_miss <- function(df){
  print("lines of missed value")
  print(table(apply(df, 1, function(x){sum(is.na(x))})))
  print("Missing value count Table:")
  apply(df, 2, function(x){sum(is.na(x))}) %>% as.data.frame
}

report_miss(bank)

bank %<>% mutate(y=as.factor(y))
```


#### Visualize missing value
- https://www.sohu.com/a/275318909_777125

#### Random Forest Scheme:
```{r}
bank_rffixed <- missForest(
  bank %>% as.data.frame, 
  verbose = T, ntree = 15,
  maxiter = 5)
bank_rffixed <- bank_rffixed$ximp %>% as_tibble
report_miss(bank_rffixed)
```

#### Modes Scheme
```{r}
treat_temp = c()
for(i in colnames(bank)){
  if(NA %in% (bank %>% distinct_at(i) %>% pull(1))){
    treat_temp %<>% append(i)
  }
}

Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

bank %>% mutate_at(
  vars(treat_temp),
  funs(ifelse(is.na(.),Mode(na.omit(.)),.))) -> bank_modefixed

report_miss(bank_modefixed)

```

#### Avering fixed Scheme:
```{r}
bank_pmmfixedesult <- mice(bank, m = 10, method='pmm', maxit=3, seed=123)
bank_pmmfixed <- mice(bank, m = 10, method='pmm', maxit=3, seed=123)

```

## Features visulization:
```{r}
#install.packages("corrplot")
library(corrplot)
temp = bank_rffixed
bank %>% dplyr::select(where(is.numeric)) %>%
  cor() -> cor_matrix

cor_matrix %>% corrplot(method = "ellipse", addCoef.col = "grey")

corrplot(cor_matrix,method = "ellipse",type = "upper") #, tl.pos = "d" #order = "hclust"
corrplot(cor_matrix,type = "lower",addCoef.col = "grey", method = "square", diag = FALSE)  #,  cl.pos = "n"
```

```{r}
inspect_cor(bank, show_plot = TRUE)
```

## Data Export:
```{r}
save(bank, bank_modefixed, bank_rffixed, bank_pmmfixed, file="../data/working/bank.RData")
```

```{r}
bank %>% summarise_all(~is.na())
```